---
title: "STAT 545B Assignment 1"
output: github_document
---

Ruichen Yao

84951482

# Exercise 1: Make a Function / Exercise 2: Document your Function

## Setup

Begin by loading data and the tidyverse package below:

```{r, message = FALSE}
library(datateachr) # <- might contain the data you picked!
library(tidyverse)
library(dplyr)
library(ggplot2)
library(testthat)

```

In previous projects, I often used the year_since_built variable to analyze problems, but there is only the year_built variable in apt_buildings. As time goes by, we need to frequently modify this variable year_since_built, so I wrote a function to directly add a variable and only modify the input every year.

```{r}
#' Add new variable year_since_built in apt_buildings dataset
#' 
#' @details
#' Add new variable year_since_built to apt_buildings dataset. It can also be edited when the new year comes. For example, just run the function again when the year 2024 arrives and replace the input with 2024.
#' 
#' @param this_year a number. This should be the number of the current AD year, for example 2023.

#' @return a selected dataset that only contains year_built and year_since_built in the apt_buildings for visual.


add_year_since_built <- function(this_year) {
  # Check if the input_year is a numeric value
  if (!is.numeric(this_year)) {
    stop("Error: Input year must be a numeric value.")
  }
  
  # Check if the input is an integer
  if (!all(as.integer(this_year) == this_year)) {
    stop("Error: Input year must be an integer.")
  }

  # Calculate the year_since_built variable
  apt_buildings$year_since_built <- this_year - apt_buildings$year_built
  
  # Check if year_since_built has been added to the dataset
  if (!("year_since_built" %in% names(apt_buildings))) {
    stop("Error: 'year_since_built' variable was not successfully added to the dataset.")
  }

  return(apt_buildings[, c("year_built", "year_since_built"), drop = FALSE])
}

add_year_since_built
```

# Exercise 3: Include examples

## Example 1: this year = 2023

```{r}
Example1 <- add_year_since_built(2023)
Example1
```

## Example 2: The new year is coming. this year = 2024

```{r}
Example2 <- add_year_since_built(2024)
Example2
```

## Example 3: Error case. Enter a string not number

```{r error=TRUE}

Example3 <- add_year_since_built("newyear")
stop("This is a deliberate error for demonstration purposes.")

```

# Exercise 4: Test the Function

```{r}

# Define a test context
test_that("add_year_since_built function tests", {
  # Test 1: Valid numeric input
  this_year_2023 <- 2023
  test1 <- add_year_since_built(this_year_2023)
  expect_true(is.numeric(test1$year_since_built))
  expect_equal(nrow(test1), nrow(apt_buildings))
  
  # Test 2: Numeric input with NAs
  this_year_empty <- NA
  expect_error(add_year_since_built(this_year_empty), "Error: Input year must be a numeric value.")
  
  # Test 3: Vector of a different type (if relevant)
  this_year_decimal <- 2023.5
  expect_error(add_year_since_built(this_year_decimal), "Error: Input year must be an integer.")
  
  # Test 4: Redundant input (providing a different number)
  this_year_2024 <- 2024
  test4 <- add_year_since_built(this_year_2024)
  expect_true(is.numeric(test4$year_since_built))
  expect_true(all(as.integer(this_year_2024) == this_year_2024))  # Check if the input is an integer
  expect_equal(nrow(test4), nrow(apt_buildings))
  
})


```
